### 2022-05-17 README.Rmd
update README badge

<!--[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/bbartholdy/byoc-starch/main?urlpath=rstudio)--> 
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5604670.svg)](https://doi.org/10.5281/zenodo.5604670)

<!-- DOI badge: [![DOI](.svg)](repo link) -->

>>>>

<!--[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/bbartholdy/byoc-starch/main?urlpath=rstudio)--> 
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5604670.svg)](https://doi.org/10.5281/zenodo.5604670)
![Current version](https://img.shields.io/github/v/release/bbartholdy/byoc-starch?label=version)
<!-- DOI badge: [![DOI](.svg)](repo link) -->
